### 2018-09-15 Sections/essay_geostrategic_quantum_politics.tex
Essays reformat
more proof reading

\subsection{Geostrategic quantum politics}\index{Geostrategic quantum politics}

@@

It is foreseeable that the future quantum internet may become fractured along geo-strategic boundaries\comment{Repetition with other section?}, with players (particularly stronger ones) unwilling to provide computational leverage to strategic competitors, even though on an absolute scale they would themselves benefit, since the leverage the competitor gains may compromise their own position, for example in cryptographic applications.

>>>>

\section{Geostrategic quantum politics}\index{Geostrategic quantum politics}

@@

It is foreseeable that the future quantum internet may become fractured\index{Fracturing} along geo-strategic boundaries, with players (particularly stronger ones) unwilling to provide computational leverage to strategic competitors, even though on an absolute scale they would themselves benefit, since the leverage the competitor gains may compromise their own position, for example in cryptographic applications.
